### 2017-02-03 presentation/slides.tex
Move Global Times to Appendix
Use real appendix
Move other slides to appendix

\begin{frame}{Bandwidth Synthetic Churn}
	\begin{figure}
		\includegraphics[scale=0.68]{bandwidth-synth-churn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Local Dissemination Stretch Synthetic Churn}
	\begin{figure}
		\includegraphics[scale=1]{local-diss-stretch-synth-churn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Local Times Synthetic Churn}
	\begin{figure}
		\includegraphics[scale=1]{local-times-synth-churn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Global Times}
	\begin{figure}
		\includegraphics[scale=0.60]{global-times-nochurn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Total \si{\giga\byte} sent/received}
	\begin{table}
		\centering
		\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
			\begin{tabular}{lSSS}
				\toprule
				&& \multicolumn{2}{c}{Churn parameters} \\
				\cmidrule{3-4}
				{Protocol}&& {1 kill/minute} & {1\{kill,add\}/minute} \\
				\midrule
				\multirow{2}{*}{\epto}&{Receive}& 21.00(024) & 26.32(032)\\
				&{Sending}& 21.21(025) & 26.57(032)\\
				\midrule
				\multirow{2}{*}{\jgroups-coord}&{Receive}& 1.47(002) & 1.75(002)\\&{Sending}& 1.43(002) & 1.70(002)\\
				\midrule
				\multirow{2}{*}{\jgroups-nocoord}&{Receive}& 1.45(001) & 1.73(002)\\&{Sending}& 1.41(001) & 1.68(002)\\
				\bottomrule
			\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Total \si{\giga\byte} sent/received}
\begin{table}[hpt]
	\centering
	\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
	\begin{tabular}{lSS}
		\toprule
		&& \multicolumn{1}{c}{Churn parameters} \\
		\cmidrule{3-3}
		{Protocol}&& {Real Trace} \\
		\midrule
		\multirow{2}{*}{\epto}&{Receive}& 81.41(108)\\
		&{Sending}& 82.67(108)\\
		\midrule
		\multirow{2}{*}{\jgroups-coord}&{Receive}& 5.56(008)\\
		&{Sending}& 5.40(008)\\
		\midrule
		\multirow{2}{*}{\jgroups-nocoord}&{Receive}& 5.58(005)\\
		&{Sending}& 5.43(005)\\
		\bottomrule
	\end{tabular}
\end{table}
\end{frame}

\begin{frame}{Total events sent with a synthetic churn}
	\begin{table}
		\centering
		\sisetup{table-format=6.1, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
		\begin{tabular}{lSSS}
			\toprule
			& \multicolumn{2}{c}{Cluster parameters} \\
			\cmidrule{2-3}
			Protocol & {1 kill/minute} & {1\{kill,add\}/minute} \\
			\midrule
			\epto & 53898.5(1339) & 59798.6(1401) \\
			\jgroups-coord & 53834.7(1755) & 59507.9(2409) \\
			\jgroups-nocoord & 53830.5(2003) & 59450.5(1751) \\
			\bottomrule
		\end{tabular}
	\end{table}
\end{frame}

>>>>

\begin{frame}{Bandwidth Synthetic Churn $(100,50)$}
	\begin{figure}
		\includegraphics[scale=0.68]{bandwidth-synth-churn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Local Dissemination Stretch Synthetic Churn $(100,50)$}
	\begin{figure}
		\includegraphics[scale=1]{local-diss-stretch-synth-churn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Local Times Synthetic Churn $(100,50)$}
	\begin{figure}
		\includegraphics[scale=1]{local-times-synth-churn}
	\end{figure}
\end{frame}

@@

\begin{frame}{Total events sent with a synthetic churn $(100,50)$}
	\begin{table}
		\centering
		\sisetup{table-format=6.1, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
		\begin{tabular}{lSSS}
			\toprule
			& \multicolumn{2}{c}{Cluster parameters} \\
			\cmidrule{2-3}
			Protocol & {1 kill/minute} & {1\{kill,add\}/minute} \\
			\midrule
			\epto & 53898.5(1339) & 59798.6(1401) \\
			\jgroups-coord & 53834.7(1755) & 59507.9(2409) \\
			\jgroups-nocoord & 53830.5(2003) & 59450.5(1751) \\
			\bottomrule
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Limitations}
	\begin{itemize}
		\item Difference not strong enough at 100 peers scale
		\item High CPU usage
		\item Docker problems on AWS/GCE
	\end{itemize}
\end{frame}

\appendix

\begin{frame}{Total \si{\giga\byte} sent/received Synthetic Churn $(100,50)$}
	\begin{table}
		\centering
		\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
		\begin{tabular}{lSSS}
			\toprule
			&& \multicolumn{2}{c}{Churn parameters} \\
			\cmidrule{3-4}
			{Protocol}&& {1 kill/minute} & {1\{kill,add\}/minute} \\
			\midrule
			\multirow{2}{*}{\epto}&{Receive}& 21.00(024) & 26.32(032)\\
			&{Sending}& 21.21(025) & 26.57(032)\\
			\midrule
			\multirow{2}{*}{\jgroups-coord}&{Receive}& 1.47(002) & 1.75(002)\\&{Sending}& 1.43(002) & 1.70(002)\\
			\midrule
			\multirow{2}{*}{\jgroups-nocoord}&{Receive}& 1.45(001) & 1.73(002)\\&{Sending}& 1.41(001) & 1.68(002)\\
			\bottomrule
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Total \si{\giga\byte} sent/received Real Churn}
	\begin{table}[hpt]
		\centering
		\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
		\begin{tabular}{lSS}
			\toprule
			&& \multicolumn{1}{c}{Churn parameters} \\
			\cmidrule{3-3}
			{Protocol}&& {Real Trace} \\
			\midrule
			\multirow{2}{*}{\epto}&{Receive}& 81.41(108)\\
			&{Sending}& 82.67(108)\\
			\midrule
			\multirow{2}{*}{\jgroups-coord}&{Receive}& 5.56(008)\\
			&{Sending}& 5.40(008)\\
			\midrule
			\multirow{2}{*}{\jgroups-nocoord}&{Receive}& 5.58(005)\\
			&{Sending}& 5.43(005)\\
			\bottomrule
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Global Times}
	\begin{figure}
		\includegraphics[scale=0.65]{global-times-nochurn}
	\end{figure}
\end{frame}

@@
